MPA Gap Analysis: IUCN and AquaMaps

### 2016-01-16 data_explore/mpa_analysis.Rmd
pushing to Neptune to work - too little space on my laptop! damn R can hog some memory

``` {r set_up_base_raster}
### import AquaMaps half-degree loiczid raster - for extents and such
rast_loiczid_file   <- file.path(dir_git, 'data/rasters/loiczid_raster.grd')
rast_loiczid        <- raster(rast_loiczid_file)
names(rast_loiczid) <- 'loiczid'

rast_base      <- raster(ext = extent(rast_loiczid), resolution = 0.01)
rast_area_base <- raster::area(rast_base) ### takes a while...

>>>>

``` {r set_up_base_raster}
### base raster will contain 0.01 degree cells from -180 to +180,
### and -90 to +90, with the associated area of each cell.
### Save it as a .tif in GitHub - about 50 
rast_base_file <- file.path(dir_git, 'data/mpa_analysis/rast_base.tif')

if(!file.exists(rast_base_file)) {
  ### import AquaMaps half-degree loiczid raster - for extents and such
  rast_loiczid_file   <- file.path(dir_git, 'data/rasters/loiczid_raster.grd')
  rast_loiczid        <- raster(rast_loiczid_file)
  names(rast_loiczid) <- 'loiczid'

  rast_empty <- raster(ext = extent(rast_loiczid), resolution = 0.01)
  rast_base  <- raster::area(rast_empty) ### takes a while...

  writeRaster(rast_base, rast_base_file)
} else {
  rast_base <- raster(rast_base_file)
}
